---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# tinkr

## Overview

__tinkr__ is an R wrapper for the Tink REST API.

Tink is a platform for open banking. Read more at their website [Tink](https://docs.tink.com/).

## Prerequisites

Sign up at [Tink](https://docs.tink.com/) to create an app. You will get a TINK_CLIENT_ID and a TINK_CLIENT_SECRET. These needs to be set in you R environment.

```{r, eval = FALSE}
# Package usethis from CRAN makes it easy to set environment variables
# install.packages("usethis")
usethis::edit_r_environ()
```

## Installation

```{r, eval = FALSE}
# Development version from GitHub:
# install.packages("devtools")
devtools::install_github("jacobferlin/tinkr")
```

## Usage

Create a `token` to authenticate yourself. A web page opens for you login to your bank. The scope argument sets what is downloaded to your app on Tink. The same page then redirects to an empty page, but the url contains a code which needs to be copied to the R console.

```{r, eval = FALSE}
library(tinkr)
token <- token(scope = c("transactions", "accounts"), market = "SE")
```

This token is used to download data from your Tink app.

```{r, eval = FALSE}
transactions(token)
accounts(token)
```
